Brownian dynamics simulation of cytoplasmic dynein's powerstroke reproduces bidirectional stepping

### 2021-07-05 papers/paper/paper.tex
More paper content

\begin{table}
  \centering
  \begin{tabular}{lrrr}
    Param & Model & Experimental & Source \\
    \hline
    $L_s$ & $\ls$ nm & $21$ nm & \cite{Burgess2003, 3vkh-cite, carter-paper}\\
    $L_t$ & $\lt$ nm & $23$ nm & \cite{Burgess2003, 3vkh-cite, carter-paper}\\
%    $\theta_b$ & $\eqb$ &  120 & \cite{leschziner} \\
    $\theta_m^{\mbox{pre}}$ & $\eqmpre$ &  197 & \cite{Burgess2003}\\
    $\theta_m^{\mbox{post}}$ & $\eqmpost$ & 242 & \cite{Burgess2003}\\
    $\theta_t$ & $\eqt$ &  & \\
    $R_t$ & $\radiust$ nm & $4$ nm & \cite{Burgess2003}\\
    $R_m$ & $\radiusm$ nm & $5.5$ nm & \cite{Burgess2003}\\
    $R_b$ & $\radiusb$ nm & $1.25$ nm & \cite{Burgess2003}\\
    \hline
  \end{tabular}
  \caption{Constant parameters used in simulation. $L_s$ and $L_t$ are the lengths of the stalk and tail interdomain linkers. The $\theta$ parameters are the equilibrium values for each angle, where $\theta_m^{\mbox{pre}}$ is the equilibrium angle for the unbound motor in pre-stroke, whereas $\theta_m^{\mbox{post}}$ is the equilibrium angle for the bound pre-stroke motor and both post-stroke motors. $R_b$, $R_m$ and $R_t$ are the MTBD, motor and tail radii. Parameters used for all simulations unless otherwise noted}
  \label{table:params}
\end{table}

@@

We present the following results from single step Brownian dynamics simulations at a constant temperature of $T=310.15$ $K$ and with a time step of $\delta t =1 * 10^{-13}$ $s$. The Monte Carlo algorithm simulated $>$18000 step cycles for each initial unsigned distance from $L_i\in [1, 72]$. The algorithm's fast computation allowed flexible optimization for each parameter in order to most accurately replicate stepping results from experiment. We investigated this parameter space by associating each stepping parameter to a property of dynein's step, observed from Yildiz's experiment. Dynein most properly demonstrated forward motility and correlated stepping when binding rates increased to promote $<$8 nm step sizes and $<$100 ns stepping times. 
%The 2-HB state dominated dynein's dwell time, while the 1-HB state happened almost instantaneous, forcing the velocity to be highly dependent on the unbding parameters. Consequently, dynein fails to equilibrate during the stepping motion and quickly rebinds shortly after unbinding.

@@

%
%\subsection*{$C$}
We determined the exponential unbinding parameter $C$ based on the likelihood for a lagging head to unbind vs. the interhead separation provided from DeWitt \textit{et. al.} \cite{dewitt}. A test for the lowest root-mean-squared error between the experiment and the model generated a value of $C=-0.35$, as shown in Figure \ref{fig:ProbLagPlot}. This parameter governs the tension-gating between dynein's heads, as the probability of a lagging step increases with $C$. All other parameters were held at the values in Table \ref{table:params}.

@@

%\subsection*{$k_b$, $k_{a}$}
The binding and affinity rates directly influenced the stepping statistics shown in Figure \ref{fig:SteppingPlots}. The binding rate controlled the tendency for immediate steps, while the affinity rate controlled the transition time from low affinity to high affinity and introduced a buffer time after unbinding to prevent instantaneous steps. This was crucial when fitting to Yildiz's slope of m = -0.4, as our model was only able to replicate the stepping correlation if dynein stepped within 8 nm 56\% of the time.

@@

Dependence of the unbinding MTBD on its relation to its partner MTBD is studied in Figure \ref{fig:tensiongating}. Figure \ref{fig:tensiongating}.a shows a heat map of initial displacement, defined as how much the stepping MTBD is ahead of the stationary MTBD, vs the step size. A line of best fit is constructed with intercept $b=5.7$ and slope $m=-1$. This indicates a negative trend where large positive displacements are likely to cause backwards steps, and negative displacements are likely to cause forward steps. This is consistent with the idea of tension gating, where tension between the two motor heads drives unbinding to relieve tension. The negative trend is reproduced in DeWitt \textit{et. al}, which shows a slope of $m=-0.4$. Figure \ref{fig:tensiongating}.b shows the unbinding probability of the lagging head with distance to the leading head. As the distance becomes greater the lagging head is more and more likely to unbind, again consistent with tension gating. This trend also very closely tracks DeWitt \textit{et. al}.

>>>>

\begin{table}
  \centering
  \begin{tabular}{lrrr}
    Param & Model & Experimental & Source \\
    \hline
    $L_s$ & $\ls$ nm & $21$ nm & \cite{Burgess2003, 3vkh-cite, carter-paper}\\
    $L_t$ & $\lt$ nm & $23$ nm & \cite{Burgess2003, 3vkh-cite, carter-paper}\\
%    $\theta_b$ & $\eqb$ &  120 & \cite{leschziner} \\
    $\theta_m^{\mbox{pre}}$ & $\eqmpre$ &  197 & \cite{Burgess2003}\\
    $\theta_m^{\mbox{post}}$ & $\eqmpost$ & 242 & \cite{Burgess2003}\\
    $\theta_t$ & $\eqt$ &  & \\
    $R_t$ & $\radiust$ nm & $4$ nm & \cite{Burgess2003}\\
    $R_m$ & $\radiusm$ nm & $5.5$ nm & \cite{Burgess2003}\\
    $R_b$ & $\radiusb$ nm & $1.25$ nm & \cite{Burgess2003}\\
    \hline
  \end{tabular}
  \caption{Constant parameters used in simulation. $L_s$ and $L_t$ are the lengths of the stalk and tail interdomain linkers. The $\theta$ parameters are the equilibrium values for each angle, where $\theta_m^{\mbox{pre}}$ is the equilibrium angle for the unbound motor in pre-stroke, whereas $\theta_m^{\mbox{post}}$ is the equilibrium angle for the bound pre-stroke motor and both post-stroke motors. $R_b$, $R_m$ and $R_t$ are the MTBD, motor and tail radii. Parameters used for all simulations unless otherwise noted}
  \label{table:constparams}
\end{table}

@@

We present the following results from single step Brownian dynamics simulations at a constant temperature of $T=310.15$ $K$ and with a time step of $\delta t =1 * 10^{-13}$ $s$. The Monte Carlo algorithm simulated $>$18000 step cycles for each initial unsigned distance of $L_i\in [1, 72]$. The algorithm's fast computation allowed flexible optimization for each parameter in order to most accurately replicate stepping results from experiment. We investigated this parameter space by associating each stepping parameter to a property of dynein's step, observed from Yildiz's experiment. Dynein most properly demonstrated forward motility and correlated stepping when binding rates increased to promote $<$8 nm step sizes and $<$100 ns stepping times. 
%The 2-HB state dominated dynein's dwell time, while the 1-HB state happened almost instantaneous, forcing the velocity to be highly dependent on the unbding parameters. Consequently, dynein fails to equilibrate during the stepping motion and quickly rebinds shortly after unbinding.

@@

%\subsection*{$k_b$, $k_{a}$}
In order to best replicate experimental observation of correlated stepping between MTBDs, we optimized the binding parameters, $k_a$ and $k_b$, according to the dependence between dynein's step and the initial MTBD positions. Figure \ref{fig:SteppingPlots} displays a heat map of initial displacement, defined as the signed distance from the stationary MTBD to the stepping MTBD, vs. the step length. Yildiz \textit{et al.} supports the idea of tension gating and displays dynein's correlated stepping from their slope of $m = -0.4$. The negative slope implies a bias for negative displacements to take forward steps while the positive displacements take negative steps. We fit $k_a$ and $k_b$ according to this slope and achieved $m = -0.492$ with values from Table \ref{table:params}. The binding parameters largely influenced the dependence between steps by influencing the rate for rebinding and controlling the tendency to equilibriate during the unbound state. More specifically, the affinity transition rate, $k_a$, controlled the transition time from high to low affinity when unbinding to introduce a buffer period and prevent instantaneous rebinding. The binding rate, $k_b$, controlled the tendency for the MTBD to rebind after being within $\epsilon$ of the MT. To achieve Yildiz's slope of -0.4, both binding rates were increased significantly to promote quick and immediate rebinding after unbinding. Lower binding rates would lessen the magnitude of the slope and lose the functionality on the MTBD separation. The bottom figure in Figure \ref{fig:SteppingPlots} shows the probability density of step lengths compared to a stepping histogram from Yildiz \textit{et al.} experiment. The peak near 0 nm displays the effect of the large binding rates, as the model was only able to replciate the desired slope if dynein preferred steps within 8 nm 56\% of the time. Despite the fast rebinding, the simulation was still able to achieve forward directionality with larger forward steps than negative ones. These results conclude that dynein must take steps within 8 nm in order to achieve proper stepping correlation between the steps and the initial MTBD separaion.

%The binding and affinity rates directly influenced the stepping statistics shown in Figure \ref{fig:SteppingPlots}. The binding rate controlled the tendency for immediate steps, while the affinity rate controlled the transition time from low affinity to high affinity and introduced a buffer time after unbinding to prevent instantaneous steps. This was crucial when fitting to Yildiz's slope of m = -0.4, as our model was only able to replicate the stepping correlation if dynein stepped within 8 nm 56\% of the time.

%
%\subsection*{$C$}
We determined the tension-gating parameter $C$ based on the likelihood for a lagging head to unbind vs. the interhead separation, provided from Yildiz \textit{et. al.} \cite{yildizpaper}. A test for the lowest root-mean-squared error between the experiment and the model generated a value of $C=-0.35$, as shown in Figure \ref{fig:ProbLagPlot}. This parameter governs the tension-gating between dynein's heads, as the probability of a lagging step increases with $C$. Consequently, $C$ does not affect the dependence on the time spent in the 2-HB state

@@

@@

%Dependence of the unbinding MTBD on its relation to its partner MTBD is studied in Figure \ref{fig:tensiongating}. Figure \ref{fig:tensiongating}.a shows a heat map of initial displacement, defined as how much the stepping MTBD is ahead of the stationary MTBD, vs the step size. A line of best fit is constructed with intercept $b=5.7$ and slope $m=-1$. This indicates a negative trend where large positive displacements are likely to cause backwards steps, and negative displacements are likely to cause forward steps. This is consistent with the idea of tension gating, where tension between the two motor heads drives unbinding to relieve tension. The negative trend is reproduced in DeWitt \textit{et. al}, which shows a slope of $m=-0.4$. Figure \ref{fig:tensiongating}.b shows the unbinding probability of the lagging head with distance to the leading head. As the distance becomes greater the lagging head is more and more likely to unbind, again consistent with tension gating. This trend also very closely tracks DeWitt \textit{et. al}.
